Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-20 cav2017/cav2017.tex

Table~\ref{table:State-space benchmarks} summarizes the list of benchmarks extracted from the literature~\cite{Franklin15,maglev,converters,CTMS}. \textit{DC Motor Position} plant provides the rotary motion that coupled with wheels and cables provides translational motion. \textit{Aircraft Pitch Dynamics} plant represents the air vehicle orientation and control based on the pitch dimension only. \textit{Ball Magnetic Levitation} plant describes the magnetic field that keeps a metal ball hanged in air.

These benchmarks were discretized with different sample times using the approach described in Appendix ~\ref{sec:appendix}. All the experiments were performed considering $x_{i}^{-}=-1$ and $x_{i}^{+}=1$ and the inputs $u_{k}=0, \forall k>0$.

>>>>

Table~\ref{table:State-space benchmarks} summarizes the list of benchmarks extracted from the literature~\cite{Franklin15,maglev,converters,CTMS}. \textit{DC Motor Position} plant describes the rotary motion that coupled with wheels and cables provides translational motion. \textit{Aircraft Pitch Dynamics} plant represents the air vehicle orientation and control based on the pitch dimension. \textit{Ball Magnetic Levitation} plant describes the magnetic field to keep a metal ball hanged in air. \textit{Buck Converter} plant represents a power converter that steps down voltage from the supply to the load while stepping up current. \textit{Boost Converter} plant also represents a power converter, but here it steps up voltage from the supply to the load while stepping down current. \textit{Buck-boost Converter} plant is a particular type of converter that has an output voltage magnitude that is either greater than or less than the input voltage magnitude. \textit{Automotive Cruise System} plant describes a system's model that represents the speed of a motor vehicle.

These benchmarks were discretized with different sample times using the approach described in the Appendix~\ref{sec:appendix}. All experiments were performed considering $x_{i}^{-}=-1$ and $x_{i}^{+}=1$ and the inputs $u_{k}=0, \forall k>0$.
